\section{Ben's Summaries}
\subsection{Studying Reddit: A Systematic Overview of Disciplines, Approaches, Methods, and Ethics}
\cite{proferes-2021}: The authors present a meta-analysis of 727 manuscripts that used Reddit as a data source (2010-2020). They discuss the manner in which data is retrieved from Reddit, the characteristics of these datasets, the communities being studied, the analytical methods used to process this data, and finally a general ethical discussion of the use of Reddit data in research. This paper presents a systematic review of \textit{how} Reddit is being used in research, the provenance / accuracy of that data, and what consequences arise from using that data.
\begin{itemize}
  \item Some Reddit communities explicitly state that approval from moderators is necessary before using their subreddit's data. There is also a need to take into account the \textit{size} of a subreddit before performing analysis on their data; smaller communities may host a more intimate and private tone, creating a space for vulnerable converstaions, and may not be as receptive to research as larger communities.
  \item One of the largest indirect known ways of accessing Reddit data is using a platform named Pushshift, ingesting data from Reddit's API for archival purposes. However, the paper states PushShift is not an exact replication of data from Reddit (another paper is cited here; further research needed).
  \item The use of Reddit data in research was steadily increasing at the time the paper was written. Within their corupus, 2017 saw 102 publications, 2018 saw 146 publications, and 2019 saw 230 publications.
  \item In terms of discipline usage of Reddit data, the author grouped disciplines into different buckets. Computer Science, Mathematics, and Engineering have the highest count of publications using Reddit data, followed by Medicine \& Health, Social Science, and then Humanities.
  \item 90.7\% of publications did not explicitly provide Reddit usernames. 69.1\% of papers did not include direct quotes from Reddit. 
  \item The data gathered from Reddit can be inherently biased due to social scoring features; "top posts" tend to receive more replies and receive more attention. Additionally, more broadly agreeable, clever, witty, or inflammatory comments are more likely to be replied to.
  \item The authors argue that researchers should carefully consider the risks presented to data subjects by including direct quotations or usernames.
\end{itemize}

\subsection{The Stories We Tell Influence the Support We Receive: Examining the Reception of Support-Seeking Messages on Reddit}
\cite{adelina-2023}: This research by Adelina et al. focuses on the interaction between support received on Reddit from advice-seekers and the textual content of their post. The methodology focused on the usage of Latent Profile Analysis. This technique focuses on 'bucketing' similar textual content into various profiles, allowing for the construction of different 'personas' that can be analysed separately. An appropriate number of profiles is essential to conducting this analysis; too many profiles may result in non-convergence, whereas too few may sacrifice accuracy. \\

Applicable to our use case, their textual preprocessing approach included cleaning and normalising Reddit data. Steps included removing posts under a specific word count (100 words), and retaining only first-level comments, removing nested replies. The authors conducted a classification analysis using several machine learning algorithms rooted on different systematic principles to obtain a holistic overview of the accuracy of their analysis. A Naïve Bayes approach and a C4.5 decision tree approach offered the higher accuracy for this task, which may be suitable to classification tasks during the implementation of this research project. \\

Interestingly, the quantity of social support received did not vary between profiles, but the \textit{quality} of the responses did. With sufficient coherence, posters who expressed negativity and low agency in their original posts tended to get more informational (advice, referral) and instrumental support (practical suggestions), whereas posts that were highly incoherent tended to receive less prescriptive support related to other profiles.
