\documentclass[a4paper,11pt]{article}

\usepackage{graphicx}  %%% for including graphics
\usepackage{url}       %%% for including URLs
\usepackage{times}
\usepackage{natbib}
\usepackage[margin=25mm]{geometry}

% NB: Is the title succinct and apt with respect to the paper content?
\title{Spontaneous Discourse in Response to Advice on Reddit}
\date{}

\author{Neimhin Robinson Gunning\\
       Trinity College Dublin\\
       16321701\\
       \texttt{nrobinso@tcd.ie}
  \and Someone Else\\
       Another Affiliation\\
       \texttt{another@email.org}
}

\begin{document}
\maketitle
% NB: Does the abstract accurately and concisely set the context for the work and indicate the main hypotheses?
\begin{abstract}
....
\end{abstract}

% NB: Are the keywords appropriate?
\textbf{Keywords:}
  advice-seeking,
  spontaneous online discourse,
  sentiment,
  affect.
\thispagestyle{empty}
\pagestyle{empty}

% NB: Does the paper present clearly the research topic and the research questions to be pursued within the paper research?
\section{Introduction}

....

% NB: Does the research review synthesize a background literature within a conceptual framework that the authors propose and defend, making clear how the research questions pursued are left open by prior literature?
% NB: Does the research question seek to relate properties of texts to qualities and quantities outside the texts with reference to an articulated theory of dependence between them?
\section{Research Review}

\cite{alfandre-2009}

\cite{brookes-2016}

\cite{smailhodzic-2016}

\cite{neviarouskaya-2010} developed a rule-based algorithm for recognizing attitude in terms of affect (negative and positive), judgement (negative and positive), and appreciation.
The algorithm systematically composes the classifications of constituent sentence parts, such that entire sentences can be classified. Their theory of attitude and the corresponding algorithm are applicable at three levels.
At the top level are just three classifications, positive, negative and neutral.
At the mid level, positive and negative classifications are further subdivided into, affect, judgement, and appreciation.
At the most fine-grained level affect is divided into interest, joy, and surprise (positive affect) and anger, disgust, fear, guilt, sadness, shame (negative affect).
The algorithm accounts for negation (by several means), amplification of sentiment, neutralisation of sentiment etc.
A corpus of human-annotated sentences is collected and compared to the results of the automated system.
The automated system was found to have greater agreement with the human annotations than a baseline system that simply selected the most intense token annotation.
\cite{neviarouskaya-2010} discuss some of the failures and failure modes of their system.
The accuracy of the automated systems (at predicting human annotations) is highest at the top level of the classification hierarchy (positive, negative, neutral), and the accuracy decreases as we move to finer grained classifications.


\cite{proferes-2021}

\cite{atkins-2010}

\cite{miller-2020}

\include{research-questions}

% NB: Does the methods section indicate clearly what corpora will be required and what sources will be adopted for the separate categories in support of answering the research questions?
% NB: Does the description of research methods indicate how the corpus will be processed in order to assess it according to the categorization scheme proposed within the paper?
% NB: Does the description of research methods indicate how the relevant quantities and qualities will be measured and assessed, stipulating what would count as a confirmation of the authors’ hypotheses and what would count as falsification of the authors’ hypotheses?
% NB: Are the research methods appropriate to the question studied?
% NB: Does the underlying research result in the assembly of a data set that will be useful to the wider research community?
\section{Methods}

% NB: Are results clearly provided?
% NB: Are tables and figures clearly annotated and captioned?
\section{Results}

\include{neimhin-summaries}

\newpage

\include{ben-summaries}

\bibliographystyle{chicago}
% NB: Does the paper present comprehensive bibliographic details for works cited?
\bibliography{mybib}

% NB: Is the paper well written in a scholarly mode of presentation?
% NB: Does the description of individual contributions suggest an equitable division of labour?

% NB: Does the description of individual contributions provide sufficiently rich description of the individual contributions in a manner that allows an independent reader to assess who contributed what and in a fashion that justifies any percentage estimates of work?
\end{document}
